Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-30 paper/main.tex
working on the rule examples

As an
example, consider mutation of Java code.  Many typical Java mutants can be
generated by the kind of ``universal'' rules (e.g., arithmetic
operator replacements) considered above.  Other mutation operators
suitable for Java source are provided by considering the set of
``C-like'' languages that use the logical operators and control
constructs common to e.g.,  Java, C, and C++ ({{\tt if}, {\tt while},
  etc.).  Statement deletion at the line level can also be implemented
  by using the common comment notation for such languages.
  Implementing Java mutation, given universal and C-like rules, may
  require no more than a handful of additional rules.

>>>>

As an
example, consider mutation of Java code.  Many typical Java mutants can be
generated by the kind of ``universal'' rules (e.g., arithmetic
operator replacements) considered above.  Other mutation operators
suitable for Java source are provided by considering the set of
``C-like'' languages that use the logical operators and control
constructs common to e.g.,  Java, C, and C++ ({{\tt if}, {\tt while},
  etc.).  Statement deletion at the line level can also be implemented
  by using the common comment notation for such languages.
  Implementing Java mutation, given universal and C-like rules, may
  require no more than a handful of additional rules.
% Just an example style, the most important is the escapeinside part, the rest... not so much. you probably have your own.
\lstdefinestyle{cstyle}{
language=c,
basicstyle=\ttfamily\bfseries\scriptsize,
  morekeywords={virtualinvoke},
  keywordstyle=\color{blue},
  ndkeywordstyle=\color{red},
  commentstyle=\color{dkred},
% https://tex.stackexchange.com/questions/329533/listings-package-lstinline-command-has-strange-spacing-behaviour-after-double-qu
  keepspaces=true,              % very important to preserve space after ' in footnote
  numbers=left,
  breaklines=true,
  numberstyle=\ttfamily\footnotesize\color{gray},
  stepnumber=1,
  numbersep=10pt,
  backgroundcolor=\color{white},
  tabsize=4,
  showspaces=false,
  showstringspaces=false,
  xleftmargin=.23in,
  captionpos=b,
  escapeinside={(?}{?)},
}

% set above style (or just use your style)
\lstset{style=cstyle}

% example listing, basically use escape inside and then do use \color and \verb
\begin{lstlisting}[basicstyle=\footnotesize\ttfamily,numbers=none]
if(strcmp((?\color{dkgreen}\verb|:[1]|?),"(?\color{dkgreen}\verb|:[2]|?)"))
\end{lstlisting}

\begin{figure*}[hbtp]
\centering
\caption{Regular Expression Rule Examples \clg{Comby, or PPC, you think?}}
\label{tab:rules}
  \begin{tabular}{ll|ll|ll}
    \hline
    \mc{2}{c|}{Universal}                          & \mc{2}{c|}{C-Like}      & \mc{2}{c|}{Language-Specific} \\
    Regexp & Comby                                 & Regexp & Comby & Regexp & Comby     \\
    {\tt < ==> >} & {\tt :[a]<:[b] ==> :[a]>:[b]}  &  {\tt  else ==>}  & {\tt  else ==>} & {\tt synchronized ==>} &  {\tt synchronized ==>} \\
    {\tt < ==> ==} & {\tt :[a]<:[b] ==> :[a]==:[b]} &  {\tt if (\textbackslash(.*\textbackslash)) ==> if (!\textbackslash 1)} &  {\tt if (:[cond]) ==> if (!(:[cond]))} & {\tt (\^{}\textbackslash s*)(\textbackslash S+.*\textbackslash n) ==> \textbackslash 1pass} & {\tt
                                                                          :[ s]:[expr]:[lf~[\textbackslash n]] ==> :[s]pass:[lf]} \\
{\tt < ==> <=}  & {\tt :[a]<:[b] ==> :[a]<=:[b]} & {\tt if (\textbackslash(.*\textbackslash)) ==> if
                 (1==1)} & {\tt if (:[cond]) ==> if (1==1)} &  {\tt any\_of ==> all\_of} & {\tt any\_of ==> all\_of} \\
\hline
\end{tabular}
\end{figure*}
